\section{Introduction}
\label{sec:theory}
% Introduction Sentence
With the increasing interconnection of all sorts of devices their management too becomes increasingly difficult. Large scale computer networks require solutions more scalable and reliable than what conventional centralized management can provide.

% Conventional algorithms and their disadvantages
Traditionally, variables of the network, such as throughput, workload and bandwidth, are gathered through the whole network by a central management system. Information is collected from all nodes of the network via periodic polling (e.g. SNMP) and stored in a database. Among several apparent drawbacks such as single point failure and performance bottleneck the most important is the inability to scale. A centralized management system cannot scale well with an increasing number of nodes, as any new node has to send its updates through the whole network. The load on the closer links increases with every additional node. In the long run this puts mission-critical business processes at risk \cite{Stadler529980}.

% Distributed algorithms as a super class
Distributed algorithms tackle these problems by propagating messages through the whole network in a more decentralized manner. Apart from dealing with the problems mentioned above they make global information locally accessible. Other components of the network can use this information to optimize their own behavior\cite{jelasity_gossip-based_2005}.

% Zooming in, the gossip algorithms
One variant of these algorithms is the Gossip-based aggregation. Gossip-based algorithms, also known as epidemic-style techniques \cite{I.Gupta2006}, are used to deal with drawback of deterministic algorithms in exchange for certainties. This algorithm is capable of aggregating global information in a completely decentralized manner \cite{jelasity_gossip-based_2005}. They differ from other distributed algorithms such as Echo algorithm proposed by Segell \cite{SegallG89} through their lack of structure. They do not require any structure of the network, other than an awareness of immediate neighbors. That said, gossip-based algorithms could be combined with tree-based algorithms to reach an optimization for some topologies \cite{KyasanurCG06}.

% The aspect we study network topology and it's influence on performance
It has previously been proven that the underlying network topology has a strong impact on the performance of gossip-based algorithm \cite{5929538, jelasity_gossip-based_2003}. Yet little work exist investigating the behavior of gossip-based aggregation in real network topologies. This study focuses on the divergence of performance in different topologies of real computer networks. To this purpose a number of networks, sharing the same number of nodes, have been chosen from an online database \cite{knight_internet_2011}.

% Goal -- UNCLEAR?!
Starting from the the problems of centralized management this study looks at the other side of the spectrum of management systems. This study aims at evaluating gossip-based aggregation in light of its dependence on network topology.

% An index of the paper
The remainder of the article is structured as follows. Section \ref{sec:theory} gives an introduction to the algorithm and our methodology. Next, section \ref{sec:implementation} presents the chosen implementation. Both the emulation of the networks and the implementation of the gossip algorithm are explained. Subsequently in section \ref{sec:result} the results of the experiment is presented. Conclusions and future work as well as related work is highlighted in section \ref{sec:conclusion}.
