\documentclass[11pt,a4paper]{scrartcl}

%\textwidth=15cm \hoffset=-1.2cm %
%\textheight=25cm \voffset=-2cm %
\pagestyle{headings}
%\parskip1ex

\date{}

\usepackage[T1]{fontenc} 
\usepackage[utf8]{inputenc} 
\usepackage[english]{babel} 
\usepackage{verbatim}
\usepackage{graphicx}
%\usepackage{amssymb}
\usepackage{acronym}
\usepackage{standalone}
\usepackage{url}
\usepackage{cite}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage{setspace}
%\usepackage[backend=bibtex]{biblatex}
%\setlength{\parskip}{\baselineskip}
\setlength{\parindent}{0pt}%
\onehalfspacing
\pagenumbering{arabic}

\def\keywords#1{\begin{center}{\bf Keywords}\\{#1}\end{center}} %

\def\titulo#1{\title{#1}} %
\def\autores#1{\author{#1}} %

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Evaluating Gossip-based aggregation\\{\LARGE An experimental study using network emulation}}
% Authors
\author{Niklas Semmler <semmler@kth.se>\\
Jiannan Guo <jiannang@kth.se>\\[0,25cm]
Supervisor: Prof. Maguire <maguire@kth.se>\\
KTH Royal Institute of Technology}%

\begin{document}
% Type down your paper title
%
\maketitle
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
% This "." is necessary to let the line start on the left
%{.} \\
\noindent\HRule \\
\begin{abstract}
\noindent This study briefly introduces the gossip algorithm and aggregation mechanism. It addresses the influence of network topologies on the performance of a gossip-based aggregation algorithm. Several analytical studies are discussed. The hypothesis, the number of links is proportional to the convergence time, is evaluated. A basic gossip-based aggregation algorthm is implemented and its performance is determined in a network emulator. Four different network topologies serve as conditions. Data is collected from the experiment and the statistical method is utilized to test the hypothesis. The results support the hypothesis and a number of possible future extension become visible.
%TODO: add conclusion
\end{abstract}
\HRule \\
\keywords{Gossip-based aggregation, network emulation}% TODO: refine keywords

%\newpage
%\tableofcontents
%\newpage

%%%%%% Begin of Chapters %%%%%%%%

\input{ch1}
\input{ch2}
\input{ch3}
\input{ch4}
\input{ch5}

%%%%%% End of Chapters %%%%%%%%%%

\bibliographystyle{ieeetr}
\bibliography{report}

\appendix


\end{document}
